Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-11-14 manuscript/acronyms.tex
add more genes
add Gene Set Enrichement acronym
discuss start of OUCH analysis
add discussion of tissue specificity index
add sra archive
add GH acronym
use PSG and PAG acronyms; update introduction
discuss go results for core placenta transcriptome
prep for genome biology submission
change capitalization of GH
switch to acro from acronym

\acrodef{EV}[EV]{Extracellular Vesicle}
\acrodef{SVM}{Support Vector Machine}
\acrodef{ROC}{Receiver Operating Characteristic}
\acrodef{KNN}{K Nearest Neighbors}
\acrodef{SRA}{Sequence Read Archive}
\acrodef{PRG2}[\textit{PRG2}]{Proteoglycan 2, bone marrow}
\acrodef{FPKM}{Fragments Per Kilobase of exon per Million reads}
\acrodef{CSH1}[\textit{CSH1}]{chorionic somatomammotropin hormone 1}
\acrodef{CSH2}[\textit{CSH2}]{chorionic somatomammotropin hormone 2}
\acrodef{CSHL1}[\textit{CSHL1}]{chorionic somatomammotropin hormone-like 1}
\acrodef{GH2}[\textit{GH2}]{growth hormone 2}

>>>>

\DeclareAcronym{EV}{short=EV,long=Extracellular Vesicle}
\DeclareAcronym{SVM}{long=Support Vector Machine}
\DeclareAcronym{ROC}{long=Receiver Operating Characteristic}
\DeclareAcronym{KNN}{long=K Nearest Neighbors}
\DeclareAcronym{SRA}{long=Sequence Read Archive}
\DeclareAcronym{PRG2}{short=\textit{PRG2},long=Proteoglycan 2, bone marrow}
\DeclareAcronym{FPKM}{long=Fragments Per Kilobase of exon per Million reads}
\DeclareAcronym{CSH1}{short=\textit{CSH1},long=chorionic somatomammotropin hormone 1}
\DeclareAcronym{CSH2}{short=\textit{CSH2},long=chorionic somatomammotropin hormone 2}
\DeclareAcronym{CSHL1}{short=\textit{CSHL1},long=chorionic somatomammotropin hormone-like 1}
\DeclareAcronym{GH2}{short=\textit{GH2},long=growth hormone 2}
\DeclareAcronym{CEA}{long=carcinoembryonic antigen}
\DeclareAcronym{HSD3B1}{short=\textit{HSD3B1},long=3-β Hydroxysteroid dehydrogenase 1}
\DeclareAcronym{GSE}{long=Gene Set Enrichment}
\DeclareAcronym{OU}{long=Ornstein-Uhlenbeck}
\DeclareAcronym{OUCH}{long=\ac{OU} Comparative Hypotheses}
\DeclareAcronym{TSI}{long=Tissue Specificity Index}
\DeclareAcronym{SRA}{long=Sequence Read Archive}
\DeclareAcronym{GH}{long=Growth Hormone}
\DeclareAcronym{PSG}{long=Pregnancy-Specific Glycoprotein}
\DeclareAcronym{PAG}{long=Pregnancy-Associated Glycoprotein}
\DeclareAcronym{GO}{long=Gene Ontology}
\DeclareAcronym{FDR}{long=False Discovery Rate}
